\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-09-19 notes/2loopNLSM.tex
added intro

\setstackgap{S}{6pt}
\setstackgap{L}{7pt}

\section{Introduction}
\section{Background}
To set the stage, in this section we provide an overview of color-kinematics duality -- both the on-shell and off-shell constructions. We then explicate our approach for constructing color-dual integrands in theories for which the off-shell kinematic algebra has not yet been identified, like Yang-Mills and NLSM. 
\subsection{Color-dual Amplitudes}

@@

\subsection{Color-dual Lagrangians}
While BCJ relations is an on-shell statement about the color-dual nature of scattering amplitudes, one might aspire to hard code color-kinematics duality by realizing an off-shell Lagrangian description of the theory. The double-copy construction of \ref{DCconstruction} would suggest a manifestly cubic Lagrangian of the form:
\be
\mathcal{L} = P_V^{ab}P_W^{ij}\mathcal{O}^a_i \Box \mathcal{O}^b_j +  V^{abc} W^{ijk}\mathcal{O}^a_i \mathcal{O}^b_j \mathcal{O}^c_k
\ee
where $V^{abc}$ and $W^{ijk}$ are cubic Feynman rules mixing field operators $\mathcal{O}^{a}_i$ indexed by quantum numbers $a$ and $i$. We have introduced $P_V^{ab}$ and $P_W^{ij}$ projection operators to encode non-local kinetic structure that could in principle participate in the construction. Should the off-shell Feynman rules of this cubic theory be antisymmetric and satisfy Jacobi identities on all internal edges,
\begin{align}
\textit{anti-symmetry}:& \quad{}_{a_1}\langle V^{a_2} \rangle_{a_3}+\text{cyc}(23)=0\,,
\\
\textit{Jacobi identity}:& \quad {}_{a_1}\langle V^{a_2} V^{a_3}\rangle_{a_4}+\text{cyc}(234)=0\,,
\end{align}
where 
\be
{}_{a_1}\langle V^{a_2}V^{a_3}\cdots V^{a_{n-1}} \rangle_{a_n} \equiv V^{a_1a_2b_1}V^{b_1a_3b_2}\cdots V^{b_{n-3} a_{n-2}a_n}\,.
\ee
This is a sufficient condition of the amplitudes to obey BCJ relations. Off-shell desciription of color-dual theories are rare, and only a few examples are available in the literature. Typically when one goes about construction color-dual theories directly from a set of cubic interactions, higher point Jacobi and antisymmetry constraints require introducing additional operators. See refs \cite{} for some recent examples. Indeed, as we'll show in \cref{sec:cubic}, Yang-Mills requires introducing a cubic 2-form interaction in order to manifest the kinematic algebra just at four-point. Absent information about the kinematic algebra, one can make progress in the construction of loop-level color-dual amplitudes by employing a color-dual bootstrap. 
\subsection{Color-dual Bootstrap}
\label{sec:bootstrap}

@@

As one can see above, the Jacobi identity of \ref{cubicJac} fails only in terms with two factors of polarization dot products, $(\varepsilon\varepsilon)^2$. Whereas, if we restricted ourselves to just considering factors with a single polarization dot product, the Jacobi identity of Yang-Mills would be satisfied \textit{off-shell} and in arbitrary spacetime dimensions:
\be
{}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4\big|^{(\varepsilon\varepsilon)^1}+\text{cyc}(234) =0
\ee
Thus for our approach at one-loop, we aim to build color-dual integrands directly from kinematic factors of this form. The organizational principle underlying this construction can be easily understood in terms of a polarization decomposition of vector amplitudes introduced by one of the authors \cite{Pavao:2022kog}, which we summarize briefly below. 
\subsection{Block Decomposition of Yang-Mills}
The $D$-dimensional Lagrangians of \ref{} can be understood as selecting specific on shell states to isolate the cubic sector of Yang-Mills at a given loop order. Start with reducible amplitude block decomp from Ref. \cite{Pavao:2022kog}:
\begin{equation}\label{eq:pureVecRABD}
A_{(\sigma)}^{\text{YM}} = \sum_{k=0}^{\lfloor |\sigma|/2\rfloor}\sum_{\rho \in S^{2|k}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
\end{equation}
By a simple mass-dimensioin argument, we know the tree-level cubic sector must be at $\mathcal{O}((\varepsilon\varepsilon)^1)$:
\be
A_{(\text{tree})}^{\text{cubic}} = \sum_{\rho \in S^{2|1}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
\ee
while at one-loop, the cubic sector corresponds to $\mathcal{O}((\varepsilon\varepsilon)^0)$ in polarization dot products:
\be
A_{(\text{1-loop})}^{\text{cubic}} = \sum_{\rho \in S^{2|0}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
\ee
When decomposed in this way, in order for the full amplitude to be gauge invariant, the polarization stripped building blocks, must obey a set of Ward-Identities between different helicity sectors:
 \begin{equation}\label{eq:GIrelA}
\Delta_{(\sigma)}^{(\rho)}\Big|_{\epsilon_i\rightarrow k_i} =-
\sum_{j \in \rho^c} (k_i \varepsilon_j)\Delta_{(\sigma )}^{(\rho\cup (ij))} \,.
\end{equation}
With this in hand, we can construct a Lagrangian description of the of the cubic sector for Yang-Mills, and will demonstrate that the resulting amplitudes with manifestly color-dual Feynman rules are equivalent to both SDYM and NLSM through one-loop. 
\subsection{Semi-abelian Yang-Mills theory}
As we demonstrate above, if we include factors of $(\varepsilon\varepsilon)^{n\geq 1}$ at tree-level, then we need to keep the Yang-Mills four-point contact for color-kinematics duality to be restored on-shell. However, the contrapositive is also true -- if we get rid of the four-point Yang-Mills vertex, then we only need terms that contribute to the manifestly color-dual cubic sector of the theory.

@@

\subsection{One-loop color-dual integrands}
Our first application of this theory for color-dual construction at loop level is for self-dual Yang-Mills (SDYM). At tree-level, the off-shell cubic vertices can be written in terms of light cone coordinates \cite{}:
\be
X(p,k) = p_u k_w-p_w k_u
\ee
At loop-level, this construction needs to be analytically continued to general dimension in order to apply dimensional regularization at one-loop. This can be done using the cubic semi-YM vertices of the previous section:
\be
\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= \mathcal{X}(k_1,k_2) = (\varepsilon_1\varepsilon_3)(\varepsilon_2 k_3) -  (\varepsilon_2\varepsilon_3)(\varepsilon_1 k_3)
\ee
Plugging in on-shell all-plus helicity states in light-cone gauge will yield precisely the 4D SDYM vertex, up to an unphysical phase. Of course, this has the advantage of permitting a $D$-dimensional construction of the one-loop integrand. Below we provide a four-point example:
\be
\simplebox = g_{\text{YM}}^4 \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\mathcal{X}(k_3,l_3)\mathcal{X}(k_4,l_4)\rangle
\ee
where $l_i = l+k_1+k_2+\cdots+ k_i$. In general, the $n$-gon vertex would be
\be
\mathcal{N}^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = g_{\text{YM}}^n \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\cdots \mathcal{X}(k_n,l_n) \rangle
\ee
Due to the state-sum of internal loop factors, $\sum {\varepsilon_{(+l)}\varepsilon_{(-l)}}=D$, the integrand above depends explicitly on the spacetime dimension, $D$. By taking a derivative\footnote{Another way to understand this derivative is that it selects the large $D$ behavior of the integrand.}, we can recover the integrand needed for all-plus one-loop amplitudes with an internal scalar:
\be
\frac{\partial}{\partial D} \mathcal{N}^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = (2 g_{\text{YM}})^n (l_1 k_1)(l_2 k_2)\cdots (l_n k_n)
\ee
This integrand numerator with internal scalar loop is precisely what one would obtain from the Feynman rules of YZ-theory, absent the $XZ$ internal vector loop. For more background, we refer the reader to appendix \ref{}. 
\be
 \mathcal{N}^{\text{NLSM}}_{n\text{-gon}}=\left[\frac{\partial}{\partial D} \mathcal{N}^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =  f_\pi^{-n} [12][23]\cdots [n1]
\ee
Where we have define the antisymmetric kinematic variable, $[LR] = l_L^2 - l_R^2$
\subsection{Two-loop obstruction}
At two-loop, introducing terms that conspire with four-point contacts is unavoidable (add diagram). Thus, to approach the problem of two-loop construction, we employ an ansatz based approach. 
\section{Two-loop bootstrap}

\subsection{Two-loop NLSM}
\label{sec:pions}

@@

\subsection{Double-copy verification}
\ace{I'm punting a lot of discussion to Ref \cite{Carrasco:2023qgz}.
  Do we think that is a problem?}

@@

\subsection{Two-loop Yang-Mills revisited}

@@

\section{Conclusions and Outlook}
There is overwhelming evidence that YM and NLSM obey color-kinematics duality at loop level even though naive Lagrangians for these theories do not manifest the duality.
At tree level, the duality can be manifested by breaking manifest Bose symmetry at the Lagrangian level, either by explicitly picking different gluon states (as in SDYM) or by picking states that only restore Bose symmetry in the final amplitude (as in NLSM).
All of these theories can be encapsulated in the semi-Abelian YM theory presented in \cref{eq:semiYM} which obscures the Bose symmetry of the external states due to the presence of the two gauge fields $A_\mu$ and $\bar{A}_\mu$.
The kinetic mixing between the two gauge fields permits globally color-dual 1-loop integrands, but special care must be taken so that the integrands produced from semi-Abelian YM correspond to SDYM or NLSM.
Due to the kinetic mixing that stems from the broken Bose symmetry, it is impossible to construct a 2-loop integrand for semi-Abelian YM theory, that is, the theory is 1-loop exact.
Obtaining a globally color-dual integrand beyond 1-loop then requires sacrificing more than just Bose symmetry and in this paper it is argued that off-shell locality must be abandoned.\footnote{Locality is relaxed in \cite{Mogull:2015adi} in order to obtain color-dual 2-loop integrands.}

@@

\subsection{Non-local construction of scattering amplitudes}

@@

\subsection{Non-local construction of color-dual integrands}

@@

\section{Spinor-helicity and conventions}
\jm{I would be happy to say that we use a mostly minus metric and the spinor helicity conventions of \cite{jjmcTASI2014} in the introduction and omit this appendix.}

Here we apply the same conventions of Ref.~\cite{jjmcTASI2014}, which we quote now. For massless momenta, $k_a$ and $k_b$, we have 
\begin{equation}
s_{ab} = (k_a+k_b)^2= \langle ab \rangle[ba]\,,
\end{equation}
the component definition of our spinor bracket that are consistent with the conventions above,
\begin{align}
\langle ab \rangle &= \frac{(a_1 + i a_2)(b_0+b_3)-(b_1 + i b_2)(a_0+a_3)}{\sqrt{(a_0+a_3)(b_0+b_3)}}\,,
\\
[ab] &= \frac{(b_1 - i b_2)(a_0+a_3)-(a_1 - i a_2)(b_0+b_3)}{\sqrt{(a_0+a_3)(b_0+b_3)}}\,,
\end{align}
where the $a_i$ are component values of the four-vector, $k^\mu_a = (a_0,a_1,a_2,a_3)$. Four-dimensional polarization dot products with fixed helicity states can be mapped as follows:
\begin{equation}\label{eq:4DPols}
\begin{aligned}
k_a \cdot \varepsilon_b^{(+)} &= \frac{\langle q a \rangle[ab]}{\sqrt{2}\langle q b\rangle}\,,
\qquad\quad \qquad
k_a \cdot \varepsilon_b^{(-)} = -\frac{[qa]\langle ab\rangle}{\sqrt{2}[qb]}\,,
\\
\varepsilon_a^{(-)}\cdot \varepsilon_b^{(+)} &= - \frac{\langle q a\rangle [qb]}{ [qa]\langle q b\rangle} \,,
\qquad \qquad
\varepsilon_a^{(\pm)}\cdot \varepsilon_b^{(\pm)} = 0 \,,
\end{aligned}
\end{equation}
Note that given the above definition, the spinor helicity variables carry the same mass dimension for both the angle and square brackets. In terms of light-cone coordinates that we employed in the text, the angles and squares can be rewritten as follows:
\begin{align}
\langle ab \rangle &= \frac{a_w b_u-a_u b_w}{\sqrt{a_ub_u}}\,,
\\
[ab] &= \frac{b_{\bar{w}}a_u-a_{\bar{w}}b_u}{\sqrt{a_ub_u}}\,,
\end{align}
The conventions we use in the text where the holomorphic spinor cares extra mass dimension essentially amounts to shifting the bracket by the following:
\begin{align}
\langle ab \rangle &\rightarrow a_w b_u-a_u b_w \equiv X(a,b)\,,
\\
[ab] &\rightarrow \frac{b_{\bar{w}}a_u-a_{\bar{w}}b_u}{a_ub_u}\equiv Q(a,b)\,,
\end{align}
With this, we still obtain the same completeness relation for the SDYM spinors:
\be
X(a,b)Q(b,a) = \frac{1}{2}s_{ab}
\ee
\section{Regulating BEL integrals}
At one-loop, weight counting tells us that the $n$-gon master numerator must have $n$ on-shell $Z$-particles. Unitarity requires that there are three distinct contributions from $Y\!Z$ theory -- the first from an off-shell $Y$-loop particle and then two more from different orientations of a $\bar{Z}Z$-loop.  Thus, $Y\!Z$ theory gives us the following one-loop $n$-gon numerator:
\be
N^{n\text{-gon},YZ}_{(12...n)} = (T^{1}T^{2}\cdots T^{n})+2\, (F^1F^2\cdots F^n)
\ee
where $(\,\cdots)$ indicates an internal contraction over the $YY$ and $\bar{Z}Z$ loops. Plugging in the Feynman rule of \cref{eq:FeynmanRuleYYZ} and \cref{eq:FeynmanRuleXZZ}, we can readily obtain expressions in terms of the internal loop factors $l_i$ and the external momenta $k_i$ (we define the $l_i$ loop momentum as that flowing into $k_i$ and out of $k_{i-1}$):
\be
N_{(12...n)}^{\text{NLSM}}=(T^{1}T^{2}\cdots T^{n}) = (l_1 k_1)(l_2 k_2) \cdots (l_n k_n)
\ee
and similarly so for the internal vector contribution:
\be
 (F^1F^2\cdots F^n) = (D-4)(l_1 k_1)(l_2 k_2) \cdots (l_n k_n) + \mathcal{O}(D^0)
\ee
The dimension dependent factor essentially counts that number of internal vector states. While this $n$-gon is manifestly color-dual, it does not produce the right cuts for NLSM. However, the scalar contribution, that comes dressed with an overall factor $(D-4)$ \textit{does} manifest the duality globally, and satisfies all the desired pion cuts. In order for the Feynman rules for $Y\!Z$ theory compute one-loop color-dual numerators consistent with NLSM cuts, we must add some additional states to cancel off he spurious poles, while preserving color-kinematics duality. We leave this as a direction of future work.

>>>>

\setstackgap{S}{6pt}
\setstackgap{L}{7pt}
\newpage
\section{Introduction}\label{intro}
Since the turn of the century, our understanding of the $S$-matrix and its hidden structure has expanded dramatically. At the heart of this progress is the mantra that physical observables are simpler when studied on-shell. However, while plugging in on-shell states certainly offers a path towards taming the factorial growth of Feynman diagrams, it also obscures the off-shell structure at the heart of many quantum field theories. A shining example of this hidden structure is the duality between color and kinematics \cite{BCJ}, which states that the kinematic numerators of gauge theory amplitudes can be rearranged to obey the same algebraic identities as the constituent color factors. When this duality is realized globally off-shell, it dramatically decreases the combinatorial complexity posed by integrand construction, and offers a path towards efficient assembly of quantum gravity integrands directly from simpler gauge theory building blocks via the double copy \cite{}.

However, despite the tremendous success in leveraging this duality to compute gauge and gravity observables to high orders in perturbation theory \cite{}, the duality between color and kinematics remains a conjecture at loop level. Indeed, there are many examples in the literature where identifying color-dual representations beyond one-loop has posed a formidable challenge \cite{}. In this work, we use the nonlinear sigma model (NLSM) and Yang-Mills, two theories proven to permit color-dual representations at tree-level \cite{}, as case studies for advancing our understanding of the kinematic algebra to the multi-loop level.

We begin by providing background on the duality between color

In contrast to presently available on two-loop construction of color-dual integrands \cite{}, our results are completely agnostic to the spacetime dimension; all the polarizations and momenta appearing in our construction will remain formally $D$-dimensional. This makes our methods and results particularly well suited or tackling  We are able to achieve this by employing a custom solver, \texttt{FiniteFieldSolve}, which will soon be made public. 
 \section{Background}\label{background}
To set the stage, in this section we provide an overview of color-kinematics duality -- both the on-shell and off-shell constructions. We then explicate our approach for constructing color-dual integrands in theories for which the off-shell kinematic algebra has not yet been identified, like Yang-Mills and NLSM. 
\subsection{Color-dual Amplitudes}\label{onShellCK}

@@

\subsection{Color-dual Lagrangians}\label{offShellCK}
While BCJ relations is an on-shell statement about the color-dual nature of scattering amplitudes, one might aspire to hard code color-kinematics duality by realizing an off-shell Lagrangian description of the theory. The double-copy construction of \ref{DCconstruction} would suggest a manifestly cubic Lagrangian of the form:
\be
\mathcal{L} = P_V^{ab}P_W^{ij}\mathcal{O}^a_i \Box \mathcal{O}^b_j +  V^{abc} W^{ijk}\mathcal{O}^a_i \mathcal{O}^b_j \mathcal{O}^c_k
\ee
where $V^{abc}$ and $W^{ijk}$ are cubic Feynman rules mixing field operators $\mathcal{O}^{a}_i$ indexed by quantum numbers $a$ and $i$. We have introduced $P_V^{ab}$ and $P_W^{ij}$ projection operators to encode non-local kinetic structure that could in principle participate in the construction. Should the off-shell Feynman rules of this cubic theory be antisymmetric and satisfy Jacobi identities on all internal edges,
\begin{align}
\textit{anti-symmetry}:& \quad{}_{a_1}\langle V^{a_2} \rangle_{a_3}+\text{cyc}(23)=0\,,
\\
\textit{Jacobi identity}:& \quad {}_{a_1}\langle V^{a_2} V^{a_3}\rangle_{a_4}+\text{cyc}(234)=0\,,
\end{align}
where 
\be
{}_{a_1}\langle V^{a_2}V^{a_3}\cdots V^{a_{n-1}} \rangle_{a_n} \equiv V^{a_1a_2b_1}V^{b_1a_3b_2}\cdots V^{b_{n-3} a_{n-2}a_n}\,.
\ee
This is a sufficient condition of the amplitudes to obey BCJ relations. Off-shell description of color-dual theories are rare, and only a few examples are available in the literature. Typically when one goes about construction color-dual theories directly from a set of cubic interactions, higher point Jacobi and antisymmetry constraints require introducing additional operators. See refs \cite{} for some recent examples. Indeed, as we'll show in \cref{sec:cubic}, Yang-Mills requires introducing a cubic 2-form interaction in order to manifest the kinematic algebra just at four-point. Absent information about the kinematic algebra, one can make progress in the construction of loop-level color-dual amplitudes by employing a color-dual bootstrap. 
\subsection{Color-dual Bootstrap}
\label{sec:bootstrap}

@@

As one can see above, the Jacobi identity of \ref{cubicJac} fails only in terms with two factors of polarization dot products, $(\varepsilon\varepsilon)^2$. Whereas, if we restricted ourselves to just considering factors with a single polarization dot product, the Jacobi identity of Yang-Mills would be satisfied \textit{off-shell} and in arbitrary spacetime dimensions:
\be
{}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4\big|^{(\varepsilon\varepsilon)^1}+\text{cyc}(234) =0
\ee
Thus for our approach at one-loop, we aim to build color-dual integrands directly from kinematic factors of this form. The organizational principle underlying this construction can be easily understood in terms of a polarization decomposition of vector amplitudes introduced by one of the authors \cite{Pavao:2022kog}, which we summarize briefly below. 
\subsection{Block Decomposition of Yang-Mills}
The $D$-dimensional Lagrangians of \ref{} can be understood as selecting specific on shell states to isolate the cubic sector of Yang-Mills at a given loop order. Start with reducible amplitude block decomp from Ref. \cite{Pavao:2022kog}:
\begin{equation}\label{eq:pureVecRABD}
A_{(\sigma)}^{\text{YM}} = \sum_{k=0}^{\lfloor |\sigma|/2\rfloor}\sum_{\rho \in S^{2|k}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
\end{equation}
By a simple mass-dimensioin argument, we know the tree-level cubic sector must be at $\mathcal{O}((\varepsilon\varepsilon)^1)$:
\be
A_{(\text{tree})}^{\text{cubic}} = \sum_{\rho \in S^{2|1}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
\ee
while at one-loop, the cubic sector corresponds to $\mathcal{O}((\varepsilon\varepsilon)^0)$ in polarization dot products:
\be
A_{(\text{1-loop})}^{\text{cubic}} = \sum_{\rho \in S^{2|0}_{\sigma}}\varepsilon_{(\rho)} \Delta_{(\sigma)}^{(\rho)}\,.
\ee
When decomposed in this way, in order for the full amplitude to be gauge invariant, the polarization stripped building blocks, must obey a set of Ward-Identities between different helicity sectors:
 \begin{equation}\label{eq:GIrelA}
\Delta_{(\sigma)}^{(\rho)}\Big|_{\epsilon_i\rightarrow k_i} =-
\sum_{j \in \rho^c} (k_i \varepsilon_j)\Delta_{(\sigma )}^{(\rho\cup (ij))} \,.
\end{equation}
With this in hand, we can construct a Lagrangian description of the of the cubic sector for Yang-Mills, and will demonstrate that the resulting amplitudes with manifestly color-dual Feynman rules are equivalent to both SDYM and NLSM through one-loop. 
\subsection{Semi-abelian Yang-Mills theory}\label{semiYM}
As we demonstrate above, if we include factors of $(\varepsilon\varepsilon)^{n\geq 1}$ at tree-level, then we need to keep the Yang-Mills four-point contact for color-kinematics duality to be restored on-shell. However, the contrapositive is also true -- if we get rid of the four-point Yang-Mills vertex, then we only need terms that contribute to the manifestly color-dual cubic sector of the theory.

@@

\subsection{One-loop color-dual integrands}\label{oneLoopCK}
Our first application of this theory for color-dual construction at loop level is for self-dual Yang-Mills (SDYM). At tree-level, the off-shell cubic vertices can be written in terms of light cone coordinates \cite{}:
\be
X(p,k) = p_u k_w-p_w k_u
\ee
At loop-level, this construction needs to be analytically continued to general dimension in order to apply dimensional regularization at one-loop. This can be done using the cubic semi-YM vertices of the previous section:
\be
\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= \mathcal{X}(k_1,k_2) = (\varepsilon_1\varepsilon_3)(\varepsilon_2 k_3) -  (\varepsilon_2\varepsilon_3)(\varepsilon_1 k_3)
\ee
Plugging in on-shell all-plus helicity states in light-cone gauge will yield precisely the 4D SDYM vertex, up to an unphysical phase. Of course, this has the advantage of permitting a $D$-dimensional construction of the one-loop integrand. Below we provide a four-point example:
\be
\simplebox = g_{\text{YM}}^4 \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\mathcal{X}(k_3,l_3)\mathcal{X}(k_4,l_4)\rangle
\ee
where $l_i = l+k_1+k_2+\cdots+ k_i$. In general, the $n$-gon vertex would be
\be
\mathcal{N}^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = g_{\text{YM}}^n \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\cdots \mathcal{X}(k_n,l_n) \rangle
\ee
Due to the state-sum of internal loop factors, $\sum {\varepsilon_{(+l)}\varepsilon_{(-l)}}=D$, the integrand above depends explicitly on the spacetime dimension, $D$. By taking a derivative\footnote{Another way to understand this derivative is that it selects the large $D$ behavior of the integrand.}, we can recover the integrand needed for all-plus one-loop amplitudes with an internal scalar:
\be
\frac{\partial}{\partial D} \mathcal{N}^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = (2 g_{\text{YM}})^n (l_1 k_1)(l_2 k_2)\cdots (l_n k_n)
\ee
This integrand numerator with internal scalar loop is precisely what one would obtain from the Feynman rules of YZ-theory, absent the $XZ$ internal vector loop. For more background, we refer the reader to appendix \ref{}. 
\be
 \mathcal{N}^{\text{NLSM}}_{n\text{-gon}}=\left[\frac{\partial}{\partial D} \mathcal{N}^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =  f_\pi^{-n} [12][23]\cdots [n1]
\ee
Where we have define the antisymmetric kinematic variable, $[LR] = l_L^2 - l_R^2$
\subsection{Two-loop obstruction}\label{2LoopObstruction}
At two-loop, introducing terms that conspire with four-point contacts is unavoidable (add diagram). Thus, to approach the problem of two-loop construction, we employ an ansatz based approach. 
\section{Two-loop bootstrap}\label{2loopBoot}

\subsection{Two-loop NLSM}\label{2loopNLSM}
\label{sec:pions}

@@

\subsection{Double-copy verification}\label{doubleCopyVerify}
\ace{I'm punting a lot of discussion to Ref \cite{Carrasco:2023qgz}.
  Do we think that is a problem?}

@@

\subsection{Two-loop Yang-Mills revisited}\label{2loopYM}

@@

\section{Conclusions and Outlook}\label{conclusions}
There is overwhelming evidence that YM and NLSM obey color-kinematics duality at loop level even though naive Lagrangians for these theories do not manifest the duality.
At tree level, the duality can be manifested by breaking manifest Bose symmetry at the Lagrangian level, either by explicitly picking different gluon states (as in SDYM) or by picking states that only restore Bose symmetry in the final amplitude (as in NLSM).
All of these theories can be encapsulated in the semi-Abelian YM theory presented in \cref{eq:semiYM} which obscures the Bose symmetry of the external states due to the presence of the two gauge fields $A_\mu$ and $\bar{A}_\mu$.
The kinetic mixing between the two gauge fields permits globally color-dual 1-loop integrands, but special care must be taken so that the integrands produced from semi-Abelian YM correspond to SDYM or NLSM.
Due to the kinetic mixing that stems from the broken Bose symmetry, it is impossible to construct a 2-loop integrand for semi-Abelian YM theory, that is, the theory is 1-loop exact.
Obtaining a globally color-dual integrand beyond 1-loop then requires sacrificing more than just Bose symmetry and in this paper it is argued that off-shell locality must be abandoned.\footnote{Locality is relaxed in \cite{Mogull:2015adi} in order to obtain color-dual 2-loop integrands.}

@@

\subsection{Non-local construction of scattering amplitudes}\label{nonLocalScattering}

@@

\subsection{Non-local construction of color-dual integrands}\label{nonLocalLoops}

@@

\section{Spinor-helicity and conventions}\label{Conventions}
\jm{I would be happy to say that we use a mostly minus metric and the spinor helicity conventions of \cite{jjmcTASI2014} in the introduction and omit this appendix.}

Here we apply the same conventions of Ref.~\cite{jjmcTASI2014}, which we quote now. For massless momenta, $k_a$ and $k_b$, we have 
\begin{equation}
s_{ab} = (k_a+k_b)^2= \langle ab \rangle[ba]\,,
\end{equation}
the component definition of our spinor bracket that are consistent with the conventions above,
\begin{align}
\langle ab \rangle &= \frac{(a_1 + i a_2)(b_0+b_3)-(b_1 + i b_2)(a_0+a_3)}{\sqrt{(a_0+a_3)(b_0+b_3)}}\,,
\\
[ab] &= \frac{(b_1 - i b_2)(a_0+a_3)-(a_1 - i a_2)(b_0+b_3)}{\sqrt{(a_0+a_3)(b_0+b_3)}}\,,
\end{align}
where the $a_i$ are component values of the four-vector, $k^\mu_a = (a_0,a_1,a_2,a_3)$. Four-dimensional polarization dot products with fixed helicity states can be mapped as follows:
\begin{equation}\label{eq:4DPols}
\begin{aligned}
k_a \cdot \varepsilon_b^{(+)} &= \frac{\langle q a \rangle[ab]}{\sqrt{2}\langle q b\rangle}\,,
\qquad\quad \qquad
k_a \cdot \varepsilon_b^{(-)} = -\frac{[qa]\langle ab\rangle}{\sqrt{2}[qb]}\,,
\\
\varepsilon_a^{(-)}\cdot \varepsilon_b^{(+)} &= - \frac{\langle q a\rangle [qb]}{ [qa]\langle q b\rangle} \,,
\qquad \qquad
\varepsilon_a^{(\pm)}\cdot \varepsilon_b^{(\pm)} = 0 \,,
\end{aligned}
\end{equation}
Note that given the above definition, the spinor helicity variables carry the same mass dimension for both the angle and square brackets. In terms of light-cone coordinates that we employed in the text, the angles and squares can be rewritten as follows:
\begin{align}
\langle ab \rangle &= \frac{a_w b_u-a_u b_w}{\sqrt{a_ub_u}}\,,
\\
[ab] &= \frac{b_{\bar{w}}a_u-a_{\bar{w}}b_u}{\sqrt{a_ub_u}}\,,
\end{align}
The conventions we use in the text where the holomorphic spinor cares extra mass dimension essentially amounts to shifting the bracket by the following:
\begin{align}
\langle ab \rangle &\rightarrow a_w b_u-a_u b_w \equiv X(a,b)\,,
\\
[ab] &\rightarrow \frac{b_{\bar{w}}a_u-a_{\bar{w}}b_u}{a_ub_u}\equiv Q(a,b)\,,
\end{align}
With this, we still obtain the same completeness relation for the SDYM spinors:
\be
X(a,b)Q(b,a) = \frac{1}{2}s_{ab}
\ee
\section{Regulating BEL integrals}\label{BELreg}
At one-loop, weight counting tells us that the $n$-gon master numerator must have $n$ on-shell $Z$-particles. Unitarity requires that there are three distinct contributions from $Y\!Z$ theory -- the first from an off-shell $Y$-loop particle and then two more from different orientations of a $\bar{Z}Z$-loop.  Thus, $Y\!Z$ theory gives us the following one-loop $n$-gon numerator:
\be
N^{n\text{-gon},YZ}_{(12...n)} = (T^{1}T^{2}\cdots T^{n})+2\, (F^1F^2\cdots F^n)
\ee
where $(\,\cdots)$ indicates an internal contraction over the $YY$ and $\bar{Z}Z$ loops. Plugging in the Feynman rule of \cref{eq:FeynmanRuleYYZ} and \cref{eq:FeynmanRuleXZZ}, we can readily obtain expressions in terms of the internal loop factors $l_i$ and the external momenta $k_i$ (we define the $l_i$ loop momentum as that flowing into $k_i$ and out of $k_{i-1}$):
\be
N_{(12...n)}^{\text{NLSM}}=(T^{1}T^{2}\cdots T^{n}) = (l_1 k_1)(l_2 k_2) \cdots (l_n k_n)
\ee
and similarly so for the internal vector contribution:
\be
 (F^1F^2\cdots F^n) = (D-4)(l_1 k_1)(l_2 k_2) \cdots (l_n k_n) + \mathcal{O}(D^0)
\ee
The dimension dependent factor essentially counts that number of internal vector states. While this $n$-gon is manifestly color-dual, it does not produce the right cuts for NLSM. However, the scalar contribution, that comes dressed with an overall factor $(D-4)$ \textit{does} manifest the duality globally, and satisfies all the desired pion cuts. In order for the Feynman rules for $Y\!Z$ theory compute one-loop color-dual numerators consistent with NLSM cuts, we must add some additional states to cancel off he spurious poles, while preserving color-kinematics duality. We leave this as a direction of future work.
